What We Eval in the Shadows

### 2021-08-12 paper/main.tex
use
Update 6.codegen

\begin{figure}[h!]
\begin{lstlisting}
 function(n,formula) {
    p <- function(x) eval(parse(text=formula))
\end{lstlisting} \caption{AdapSamp::rARS}
\end{figure}

\paragraph{Code Generation}
\Eval can be used to generate boiler plate code that would either be tedious to
write by hand or that is only known after deployment. The example uses \eval to
construct function objects that are parameterized with string \k{what}.
This is used  automatically generate R bindings to native code.

\begin{figure}[h]
\begin{lstlisting}
 function(methods,env) {
   for(what in cppMethods)
     methods[[what]] <- eval(substitute(function(...)CppObject$WHAT(...,name=what)),env)
\end{lstlisting}
  \caption{Rcpp::.makeCppMethods}
\end{figure}

@@

\begin{figure}[h]
\begin{lstlisting}
 function(...) {
   for(e in eval(substitute(alist(...)))) {
     x <- eval(e, parent.frame())
     if(!is.null(x)) break
   }
   x
 }
\end{lstlisting}
  \caption{statnet.common::NVL}
\end{figure}

@@

\begin{figure}[h]
\begin{lstlisting}
 function(..., env=parent.frame(), msg=NULL) {
    asserts <- eval(substitute(alist(...)))
    for (assertion in asserts) {
      res <- tryCatch({
        eval(assertion, env)
      }, assertError=function(e) { structure(FALSE, msg=e$message) })
\end{lstlisting}
  \caption{assertthat::see\_if}
\end{figure}

@@

\begin{figure}[h]
\begin{lstlisting}
 function(f,...,args=list(),env=parent.frame()) {
   f <- substitute(f)
   eval(make_call(f,...,args), env)
 }
\end{lstlisting}
\caption{igraph::do\_call}
\end{figure}

@@

\begin{figure}[h]
\begin{lstlisting}
 library(glue)
 greeting <- "Hello"
 glue('{greeting} World!')
 #> Hello World!
\end{lstlisting}
  \caption{glue::glue}
\end{figure}

@@

\begin{figure}[h]
\begin{lstlisting}
 function(formula, data, weights, ...) {
   Call <- match.call()
   indx <- match(c('formula', 'data', 'weights'), names(Call), nomatch=0)
   temp <- Call[c(1, indx)]
   temp[[1L]] <- quote(stats::model.frame)
   mf <- eval.parent(temp)
\end{lstlisting}
  \caption{survival::survfit.formula}
\end{figure}

@@

\begin{figure}[h]
\begin{lstlisting}
 function(x, asList, ...) eval(attr(x, "formula"))
\end{lstlisting}
  \caption{nlme::formula.pdMat}
\end{figure}

@@

\begin{figure}[h]
\begin{lstlisting}
 function() {
   env <- parent.env(environment())
   eval(parse(text=paste0('unlockBinding("s", env)')))
   assign("s", s, envir=env)
   lockBinding("s", env)
\end{lstlisting}
  \caption{aibd::scalaEnsure}
\end{figure}

>>>>

\begin{minipage}{.95\textwidth}
\medskip\underline{\c{AdapSamp::rARS}:}
\begin{lstlisting}
 function(n,formula) {
    p <- function(x) eval(parse(text=formula))
\end{lstlisting}\medskip
\end{minipage}

\paragraph{Code Generation}
\Eval can be used to generate boiler plate code that would either be tedious to
write by hand or that is only known after deployment. The example uses \eval to
automatically generate R bindings to C++ methods.

\begin{minipage}{.95\textwidth}
\medskip\underline{\c{Rcpp::.makeCppMethods}:}
\begin{lstlisting}
 function(methods,env) {
   for(what in cppMethods)
     methods[[what]] <-
       eval(substitute(function(...)CppObject$what(...)), env)
\end{lstlisting}\medskip
\end{minipage}

@@

\begin{minipage}{.95\textwidth}
\medskip\underline{\c{statnet.common::NVL}:}
\begin{lstlisting}
 function(...) {
   for(e in eval(substitute(alist(...)))) {
     x <- eval(e, parent.frame())
     if(!is.null(x)) break
   }
   x
 }
\end{lstlisting}\medskip
\end{minipage}

@@

\begin{minipage}{.95\textwidth}
  \medskip\underline{\c {assertthat::see\_if}:}
\begin{lstlisting}
 function(..., env=parent.frame(), msg=NULL) {
    asserts <- eval(substitute(alist(...)))
    for (assertion in asserts) {
      res <- tryCatch({
        eval(assertion, env)
      }, assertError=function(e) { structure(FALSE, msg=e$message) })
\end{lstlisting}\medskip
\end{minipage}

@@

\begin{minipage}{.95\textwidth}
  \medskip\underline{\c{igraph::do\_call}:}
\begin{lstlisting}
 function(f,...,args=list(),env=parent.frame()) {
   f <- substitute(f)
   eval(make_call(f,...,args), env)
 }
\end{lstlisting}\medskip
\end{minipage}

@@

\begin{minipage}{.95\textwidth}
  \medskip\underline{\c{glue::glue}:}
\begin{lstlisting}
 library(glue)
 greeting <- "Hello"
 glue('{greeting} World!')
 #> Hello World!
\end{lstlisting}\medskip
\end{minipage}

@@

\begin{minipage}{.95\textwidth}
  \medskip\underline{\c{survival::survfit.formula}:}
\begin{lstlisting}
 function(formula, data, weights, ...) {
   Call <- match.call()
   indx <- match(c('formula', 'data', 'weights'), names(Call), nomatch=0)
   temp <- Call[c(1, indx)]
   temp[[1L]] <- quote(stats::model.frame)
   mf <- eval.parent(temp)
\end{lstlisting}\medskip
\end{minipage}

@@

\begin{minipage}{.95\textwidth}
  \medskip\underline{\c{nlme::formula.pdMat}:}
\begin{lstlisting}
 function(x, asList, ...) eval(attr(x, "formula"))
\end{lstlisting}\medskip
\end{minipage}

@@

\begin{minipage}{.95\textwidth}
  \medskip\underline{\c{aibd::scalaEnsure}:}
\begin{lstlisting}
 function() {
   env <- parent.env(environment())
   eval(parse(text=paste0('unlockBinding("s", env)')))
   assign("s", s, envir=env)
   lockBinding("s", env)
\end{lstlisting}\medskip
\end{minipage}
